### 2012-06-06 docs/compilers/compilers.tex
add note about 4.7

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1--4.6.3 on Fedora (15 and 16) have a bug that 
shows up in multi-processor runs ({\tt toy\_convect} on 4 processors, for instance).
The symptom is a crash during initialization with the message that
``message sizes do not match across processes in the collective'' in a
{\tt parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue seems
to be a multiplication error in computing the size to allocate {\tt bxs}.
The bug is not present when you compile in debug mode, so it seems to be
related to optimization.
\end{itemize}

>>>>

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1--4.6.3 on Fedora (15 and 16) have a bug that 
shows up in multi-processor, multilevel runs ({\tt toy\_convect} on 4
processors, with {\tt inputs\_2d\_ml.test} for instance).  The symptom
is a crash during initialization with the message that ``message sizes
do not match across processes in the collective'' in a {\tt
parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue
seems to be a multiplication error in computing the size to allocate
{\tt bxs}.  The bug is not present when you compile in debug mode, so
it seems to be related to optimization.
\item gfortran 4.7.1 (prerelease) seems to have fixed the above issue.
\end{itemize}
